CDI Schubert

### 2017-11-10 datasets/microbiome/cdi_schubert.Rmd

@@

```{r}
# Read and clean cdi_schubert
otu_path = paste0(wd, "cdi_schubert_results/RDP/cdi_schubert.otu_table.100.denovo.rdp_assigned")
meta_path = paste0(wd, "cdi_schubert_results/cdi_schubert.metadata.txt")
labels = c("H", "nonCDI", "CDI")

@@

```{r, explore-goodrich-covariates}
var <- "logubiquity"
g <- ggplot(goodrichdat, aes(x = get(var), y = pval)) + geom_point()
g
```

@@

```{r}
g <- ggplot(goodrichdat, aes(x = get(covcol), y = pval)) + geom_point()
g
```

>>>>

  ## TODO: median read depth!

@@

```{r}
# Read and clean cdi_schubert
## TODO: less filtering! Keep as many hypotheses open as possible.
otu_path = paste0(wd, "cdi_schubert_results/RDP/cdi_schubert.otu_table.100.denovo.rdp_assigned")
meta_path = paste0(wd, "cdi_schubert_results/cdi_schubert.metadata.txt")
labels = c("H", "nonCDI", "CDI")

@@

```{r, explore-goodrich-covariates}
var <- "logubiquity"
g <- ggplot(goodrichdat, aes(x = get(var), y = logpval)) + geom_point()
g
```

@@

```{r}
g <- ggplot(goodrichdat, aes(x = get(covcol), y = logpval)) + geom_point()
g
```
